LME-MPM applied to quasi-brittle fracture.

### 2020-06-13 2020_EFM_MPM_Eigensoftening.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:1}
The presence of cracks is a violation of the continuity requirement of the
\acrfull{fem}. To overcome this issue, numerous numerical
artifacts have been proposed with the aim of reproducing such a
complex behaviour. These techniques vary from the employment of cohesive
approaches~\cite{Barenblatt,Hilleborg_1976}, \PNA{to the gradual insertion of}
cohesive elements \cite{Ortiz_1999,Pandolfi_2002,Ruiz_2000} at solid
elements boundaries, or handling arbitrary crack paths by level set
representation of the fracture surface~\cite{Belytschko_03}. The
simulation of fracture propagation in a more accurate and effective
way can be considered as one of the \PNA{ongoing goals} of the development of novel spatial discretization methods like meshfree techniques. Some
examples of it are the \acrfull{mpm}
\cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the
\acrfull{efgm} \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013}, the
\acrfull{sph} \cite{Wang_2020,Wang_2019}, the \acrfull{otm} \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or Peridynamics
\cite{HA_2011,RABCZUK_2017} among others. \\

Regarding \acrshort{mpm}, fracture \PNA{has been treated numerically through two different ways}. On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003,Nairn_2006}. \PNA{The basis of this methodology consist of the removal of} the restriction
of the single-valued velocity field close to the crack through, at least, two sets of nodes. In this method, different labels are assigned to the material points
and nodes to distinguish if they are in the same side of the crack or
not. Under this approach, crack surface is described with line segments
in 2D and triangle patches in 3D cases. The chosen criteria for crack
propagation is based on such parameters as energy release rate
analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
intensity factor or the J-integral discussed by Guo \& Nairn
(2004)\cite{Nairn_2004}. 
On the other hand, the \PNA{foundation} of the second approach is the introduction of failed
material points to describe the crack evolution. In these methods, the
formation of failed points describes the nucleation of cracks, and
thereafter its propagation and branching. Consequently, the position
of the crack does not need to be explicitly stated. This fact represents
significant advantages over the ``CRAMP''. Under this approach, the
prediction of failure evolution is computed with a decohesion model,
which has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} and
Schreyer {\it et al.}\cite{Schreyer_2002}. Successful simulations are provided within the framework of the fracture of brittle materials by Chen {\it et
  al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
\cite{Sulsky_2004}.\\

@@

\DM{delete to} a compromise between two competing objectives, a Pareto set is

@@

\section{Conclusions}
\label{sec:4}
\PNA{Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
\cite{Zhang_EE_2020}, two additional improvements have been proposed in the present research in order to 
solve the shortcomings of the original concept that Zhang {\it et al.} pointed out in the aforementioned paper \cite{Zhang_EE_2020}.

@@

Finally, for better capturing the measurement of forces made in the
laboratory, more realistic contact tools have to be
developed. Navas~\textif{et al.} demonstrate the importance of the
stiffness of the support in order to obtain accurate results of the
reaction forces. Interesting contact algorithms within the
\acrshort{mpm} methodology are available in the literature
\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:1}
\DM{The failure mechanisms of quasi-brittle materials and the  crack propagation have been studied from different fields such as materials science, structural engineering, earth science and petroleum engineering . The prediction of crack propagation has been approached with different numerical techniques. The \acrfull{fem} is widely used in industrial application. However,} the presence of cracks is a violation of the continuity requirement of the \acrfull{fem}. To overcome this issue, numerous numerical
artifacts have been proposed with the aim of reproducing such a
complex behaviour. These techniques vary from the employment of cohesive
approaches~\cite{Barenblatt,Hilleborg_1976}, \PNA{to the gradual insertion of}
cohesive elements \cite{Ortiz_1999,Pandolfi_2002,Ruiz_2000} at solid
elements boundaries, or handling arbitrary crack paths by level set
representation of the fracture surface~\cite{Belytschko_03}. The
simulation of fracture propagation in a more accurate and effective
way can be considered as one of the \PNA{ongoing goals} of the development of novel spatial discretization methods like meshfree techniques. Some
examples of it are the \acrfull{mpm}
\cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the
\acrfull{efgm} \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013}, the
\acrfull{sph} \cite{Wang_2020,Wang_2019}, the \acrfull{otm} \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or Peridynamics
\cite{HA_2011,RABCZUK_2017} among others. \\

 \DM{ Miguel...esto artículos se pueden citar pra enteder la evolución de la progración de la fractura. Hay estados del arte muy buenos entre ellos.  X-FEM with Level set
T. Nagashima, M. Sawada Development of a damage propagation analysis system based on level set XFEM using the cohesive zone model Comput Struct, 174 (2016), pp. 42-53
J. Huang An efficient morphology generation and level set representation of cementitious microstructures with arbitrarily shaped aggregates and cracks via extended finite elements
Comput Struct, 206 (2018), pp. 122-144
Y. Abdelaziz, A. Hamouine A survey of the extended finite element Comput Struct, 86 (11) (2008), pp. 1141-1151}
Regarding \acrshort{mpm}, fracture \PNA{has been treated numerically through two different ways}. On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003,Nairn_2006}. \PNA{The basis of this methodology consist of the removal of} the restriction
of the single-valued velocity field close to the crack through, at least, two sets of nodes. In this method, different labels are assigned to the material points
and nodes to distinguish if they are in the same side of the crack or
not. Under this approach, crack surface is described with line segments
in 2D and triangle patches in 3D cases. The chosen criteria for crack
propagation is based on such parameters as energy release rate
analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
intensity factor or the J-integral discussed by Guo \& Nairn
(2004)\cite{Nairn_2004}. 
On the other hand, the \PNA{foundation} of the second approach is the introduction of failed
material points to describe the crack evolution. In these methods, the
formation of failed points describes the nucleation of cracks, and
thereafter its propagation and branching. Consequently, the position
of the crack does not need to be explicitly stated. This fact represents
significant advantages over the ``CRAMP''. Under this approach, the
prediction of failure evolution is computed with a decohesion model,
which has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} and
Schreyer {\it et al.}\cite{Schreyer_2002}. Successful simulations are provided within the framework of the fracture of brittle materials by Chen {\it et
  al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
\cite{Sulsky_2004}.\\

@@

a compromise between two competing objectives, a Pareto set is

@@

\section{Conclusions}
\label{sec:4}

\DM{Cometario general: Pienso que hay que estructurar un poco la conclusión. No agregar tantas citas. Acá estás concluyendo tu trabajo. Iría de lo general a lo particular. Pondría claramente en cada parrafo cual es el aporte. Con tantas citas no queda claro que hiciste vos y que los otros. Las citas estarán puestas cuando vos comenzaste a hablar de lo que hiciete en el cuerpo del documento. Acá las citas minimas y tus aportes.
Imagino un primer parrafo asi diciendo cuales son las limitaciones ...propuesta modificable...:}

\DM{The paper proposes the eigensoftening algorithm in a \acrshort{MPM} framework for quasi-brittle materials to overcome the limitations observed in the EigenMPM \cite{Zhang_EE_2020}. The overestimation of tensile 
stress and strain peaks in the fracture mechanism of quasi-brittle materials and the stress oscillations observed with conventional \acrshort{mpm}/\acrshort{gimp} are faced.  }

\PNA{Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.} 
\cite{Zhang_EE_2020}, two additional improvements have been proposed in the present research in order to 
solve the shortcomings of the original concept that Zhang {\it et al.} pointed out in the aforementioned paper \cite{Zhang_EE_2020}. }

@@

Finally, for better capturing the measurement of forces made in the
laboratory, more realistic contact tools have to be
developed. Navas~\textif{et al.} demonstrate the importance of the
stiffness of the support in order to obtain accurate results of the
reaction forces. Interesting contact algorithms within the
\acrshort{mpm} methodology are available in the literature
\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}
